### 2018-08-25 evaluation.tex
Add content from response letter to the final version as the editor requests

>>>>

{\color{red}{
In Figure~\ref{fig:drawback} and \ref{fig:benefit},
The performance drops slightly as the matrix size increases 
under $NT \ge 16$.
The reason is that there is a synchronization point
at the end of each iteration
of the loop at layer 2 (Fig.~2).
The synchronization is an all-to-all 
communication, whose overhead is proportional to $NT^2$.
When $NT$ is 4 or 8, the overhead is small but
it increases quickly as $NT$ increases.
Performance also drops at matrix sizes that are
multiples of 1024 because
GEMM suffers from more memory contention at these sizes,.
As an example, we profiled the GEMM execution
at matrix sizes 3968 and 4096 under $NT_C=4$ and $NC=4$.
The measured bandwidth for packing A (B) are
1.44(0.89) GB/s at size 3968 and 0.81(0.44) GB/s at size 4096.
We can see that there is a big performance gap
in memory bandwidth.
Due to the organization of the DDR memory hardware,
The selected tiling factors $M_c$, $N_c$ and $K_c$
made GEMM more likely to cause memory contention at sizes
that are multiples of 1024
because the memory banks are accessed in a non-balanced manner.

In GEMM implementation, different matrix layouts (row-major/column-major)
are first canonicalized to an implementation defined form
by optionally swapping the $A$ and $B$ operands in $C=\alpha A B+\beta C$.
And matrix orientation information (transposed vs. non-transposed)
is eliminated by means of data packing.
SCP, which works after these transformations, 
does not rely on specific matrix layouts or orientations.

As other level-3 routines, e.g., TRSM, TRMM, SYMM and HEMM,
call GEMM internally, they should also benefit from SCP,
i.e., the SCP methodology can apply transparently to 
other BLAS-3 routines as well.
}}
